A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-06-20 paper/paper.tex
Get the intersection right

In \cref{figure:cumulative} we show the cumulative performance of each algorithm. The value of the
line at a given time for an algorithm shows the total number of instances which, individually, were
solved in at most that amount of time. Our sequential implementation beats VF2 for times over 0.2s,
LAD for times over 0.6s, and always beats SND.  Our parallel implementation beats VF2 for times over
0.06s, LAD for times over 0.02s, and always beats SND; parallelism gives us an overall benefit from
12ms onwards. Finally, removing supplemental graphs from our algorithm gives an improvement below 1s
(due to the cost of preprocessing), but is beneficial for longer runtimes.

>>>>

In \cref{figure:cumulative} we show the cumulative performance of each algorithm. The value of the
line at a given time for an algorithm shows the total number of instances which, individually, were
solved in at most that amount of time. Our sequential implementation beats VF2 for times over 0.2s,
LAD for times over 0.6s, and always beats SND.  Our parallel implementation beats VF2 for times over
0.06s, LAD for times over 0.02s, and always beats SND; parallelism gives us an overall benefit from
12ms onwards. Finally, removing the supplemental graphs from our sequential algorithm gives an
improvement below 10s (due to the cost of preprocessing), but is beneficial for longer runtimes.
